Figures for Paper

### 2021-07-14 paper_figures.Rmd
Update paper_figures.Rmd

## Effect of seqeuncer (read length) size on CE discovery

@@

  if(nrow(tbl) <2){
    return(NA)
  }else{
    comparison_table = table(unc13a = tbl$unc13a_detected, 
                             sequencing_platform = tbl$sequencing_platform)
    p_value = fisher.test(comparison_table)$p.value

    return(p_value)
  }
}

unc13a_data_fisher = unc13a_sequencing_platform %>% 
  filter(tissue_clean != "Thoracic_Spinal_Cord") %>% 
  split(.,list(unique(unc13a_sequencing_platform$tissue_clean), unique(unc13a_sequencing_platform$disease_group2))) %>% 
  purrr::map_df( quick_fisher, .id = "tissue_clean" ) %>% 
  melt() %>% 
  select(variable,value) %>% 
  separate(variable,sep = "\\.", into = c("tissue_clean","disease_group2"))

@@

unc13a_sequencing_platform_pct %>%
  ggplot(aes(x = plot_name, y = detection )) + 
  geom_col(fill = "firebrick") +
  labs(title = "UNC13A CE detection and sequencing platform", y = "UNC13A CE detected") + 
  facet_wrap(~disease_group2 + tissue_clean,scales = 'free_x') +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  geom_text(aes(x = 1.5, y = 1.05, label = paste0("p = ", signif(value,digits = 2) ) )) +
  theme(legend.text = element_text(size = 15))
 # scale_y_continuous(expand = c(0,0) ) 
```
## Effect of library size on CE discovery

```{r unc detection by library size  }
# library size

clean_data_table %>%
  filter(disease_tissue == T) %>% 
  mutate(inclusion_reads = UNC13A_3prime_leaf + UNC13A_5prime_1_leaf) %>% 
  mutate(unc13a_detected = ifelse(inclusion_reads > 0, yes = "+", no = "-")) %>% 
  mutate(disease_group2 = fct_relevel(disease_group2, "Control")) %>% 
  ggplot(aes(x = disease_group2,y = log10(library_size), fill = unc13a_detected)) + 
  geom_point(colour = "firebrick", size = 0.5, alpha = 0.9, position = position_jitter(width = 0.2, height = 0) ) + 
  geom_boxplot(colour = "black", outlier.colour = NA) +
  labs(title = "Library size and UNC13A CE detection ",subtitle = "Wilcox test") + 
  facet_wrap(~ tissue, scales = 'free_x') + 
  ggpubr::stat_compare_means(label = "p.format", label.x.npc = "center", method = "wilcox" ) +
  labs(y = "log10 library size", fill= "UNC13A CE detected", x = element_blank()) +
  theme(axis.text.x = element_text(size = 15)) + 
  ggpubr::theme_pubr()
```

## Effect of UNC13A TPM onCE discovery

```{r unc detection by UNC13A tpm }
# library size

clean_data_table %>%
  filter(disease_tissue == T) %>% 
  mutate(inclusion_reads = UNC13A_3prime_leaf + UNC13A_5prime_1_leaf) %>% 
  mutate(unc13a_detected = ifelse(inclusion_reads > 0, yes = "+", no = "-")) %>% 
  mutate(disease_group2 = fct_relevel(disease_group2, "Control")) %>% 
  ggplot(aes(x = disease_group2,y = UNC13A_TPM, fill = unc13a_detected)) + 
  geom_point(colour = "firebrick", size = 0.5, alpha = 0.9, position = position_jitter(width = 0.2, height = 0) ) + 
  geom_boxplot(colour = "black", outlier.colour = NA) +
  labs(title = "UNC13A TPM and UNC13A CE detection ",subtitle = "Wilcox test") + 
  facet_wrap(~ tissue, scales = 'free') + 
  ggpubr::stat_compare_means(label = "p.format", label.x.npc = "center", method = "wilcox" ) +
  labs(y = "UNC13A TPM", fill= "UNC13A CE detected", x = element_blank()) +
  theme(axis.text.x = element_text(size = 15)) + 
  ggpubr::theme_pubr()

@@

```{r rin discovery}
## effect of RIN?
clean_data_table %>%
  filter(disease_tissue == T) %>% 
  mutate(inclusion_reads = UNC13A_3prime_leaf + UNC13A_5prime_1_leaf) %>% 
  filter(!is.na(rin)) %>%
  mutate(unc13a_detected = ifelse(inclusion_reads > 0, yes = "+", no = "-") ) %>% 
    mutate(disease_group2 = fct_relevel(disease_group2, "Control")) %>% 
  ggplot(aes(x = disease_group2,y = rin, fill = unc13a_detected)) + 
  geom_point( colour = "firebrick", size = 0.5, alpha = 0.9, position = position_jitter(width = 0.2, height = 0) ) + 
   geom_boxplot(colour = "black", outlier.colour = NA) +
  labs(title = "Sample RIN and UNC13A CE detection ") + 
  facet_wrap(~ tissue, scales = 'free_x') + 
  ggpubr::stat_compare_means(label = "p.format", label.x.npc = "center") +
  labs(y = "RIN", x = element_blank(), fill = "UNC13A CE detection") +
  theme(axis.text.x = element_text(size = 15)) +
  ggpubr::theme_pubr()

```{r unc13a ce and UNC13B_TPM}
## effect of RIN?
clean_data_table %>%
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP", "ALS-TDP")) %>%
  add_count(tissue_clean,disease_group2) %>% 
  mutate(plot_name = glue::glue("{disease_group2} \n ({n})")) %>% 
  mutate(inclusion_reads = UNC13A_3prime_leaf + UNC13A_5prime_1_leaf) %>% 
  mutate(unc13a_detected = ifelse(inclusion_reads > 0, yes = "+", no = "-") ) %>% 
  ggplot(aes(x = plot_name, fill = unc13a_detected,y = UNC13B_TPM )) + 
  geom_point(size = 2,show.legend = F,pch = 21, position = position_jitterdodge(dodge.width=1,jitter.width = 0.3))+
  geom_boxplot(outlier.colour = NA) +
  labs(title = "UNC13A CE detection and UNC13B TPM",subtitle = "Wilcox test") + 
  facet_wrap(~ tissue_clean,scales = 'free') + 
  ggpubr::stat_compare_means(label = "p.signif",) +
  labs(y = "UNC13B TPM", x = "UNC13A CE detection") +
  theme(axis.text.x = element_text(size = 15)) +
  ggpubr::theme_pubr() +
  ggpubr::stat_compare_means(label = "p.format", label.x.npc = "center")
```

@@

```{r onlyshort}
boxplot_table %>%
    filter(tissue_clean %in%
               c("Frontal Cortex",
                 "Lumbar Spinal Cord",
                 "Cervical Spinal Cord",
                 "Motor Cortex",
                 "Temporal Cortex",
                 "Cerebellum") )%>%
    group_by(disease_group2,tissue_clean) %>%
    mutate(n_sample = n_distinct(sample)) %>%
    ungroup() %>%
    mutate(disease_group2 = gsub("Control", " Control",disease_group2)) %>%
    mutate(detection_name = glue::glue("{disease_group2} \n ( {n_sample} )"))  %>%
    mutate(tissue_clean = fct_relevel(tissue_clean, "Cervical Spinal Cord",
                                      "Frontal Cortex",
                                      "Lumbar Spinal Cord",
                                      "Temporal Cortex",
                                      "Motor Cortex")) %>%
    ggplot(aes(x = detection_name,
               y = inclusion_reads * 10^6,
               fill ="red")) +
    geom_boxplot(show.legend = F,position = position_dodge(preserve = "single",width = 1),outlier.colour = NA) +
    geom_point(size = 2,show.legend = F,pch = 21, position = position_jitterdodge(dodge.width=1,jitter.width = 0.3))+
    ggplot2::facet_wrap(vars(tissue_clean),scales = "free_x",nrow = 3) +
    ylab("UNC13A cryptic \n reads per million") +
    theme(text = element_text(size = 12)) +
    xlab("") +
    scale_fill_manual(values = colorblind_pal()(4)[2:4]) +
    theme_bw() +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    theme(text = element_text(size = 18))  +
    theme(legend.position = "bottom")
```

@@

## Correlation UNC13A PSI and STMN2 PSI with genotype effect - rs12973192

@@

ce_snp = clean_data_table %>%
  filter(disease_tissue == T) %>%
  filter(junction_reads_stmn2 >= 30) %>%
  filter(junction_reads_unc13a >= 30) %>%
  filter(grepl("Cortex",tissue_clean)) %>%
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>%
    mutate(rs12973192 = fct_relevel(rs12973192,
                              "C/C", "C/G", "G/G")) %>%
  filter(!grepl("Cord",tissue_clean)) %>%
  mutate(log10_stmn2 = log10(stmn_2_cryptic_psi_leaf)) %>%
    mutate(log10_unc13a = log10(unc13a_cryptic_leaf_psi)) %>%
    ggpubr::ggscatter(.,
                      x = "log10_stmn2",
                      y = "log10_unc13a",
                      color = 'rs12973192',
                      add = "reg.line", size = 3
                      ) +
    ylab("UNC13A CE PSI ") +
    xlab("STMN2 Cryptic PSI ") +
  stat_cor(aes( x = stmn_2_cryptic_psi_leaf,
                      y = unc13a_cryptic_leaf_psi,
                      color = rs12973192),
           method = 'spearman',
           cor.coef.name = 'rho',
           show.legend = FALSE,
           size = 14) +
    scale_color_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  theme(legend.title = element_blank()) +
  theme(text = element_text(size = 24),legend.text = element_text(size = 32)) +
    ylab(expression(paste("Lo", g[10], "UNC13A CE PSI"))) +
      xlab(expression(paste("Lo", g[10], "STMN2 CE PSI"))) +
  ggtitle("CE SNP (rs12973192) genotype")

@@

## Correlation UNC13A PSI and STMN2 PSI with genotype effect - rs12608932

in_snp = clean_data_table %>%
  filter(disease_tissue == T) %>%
    filter(junction_reads_stmn2 >= 30) %>%
  filter(junction_reads_unc13a >= 30) %>%
  filter(grepl("Cortex",tissue_clean)) %>%
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>%
    mutate(rs12608932 = fct_relevel(rs12608932,
                              "A/A", "A/C", "C/C")) %>%
  filter(!grepl("Cord",tissue_clean)) %>%
  mutate(log10_stmn2 = log10(stmn_2_cryptic_psi_leaf)) %>%
    mutate(log10_unc13a = log10(unc13a_cryptic_leaf_psi)) %>%
    ggpubr::ggscatter(.,
                      x = "log10_stmn2",
                      y = "log10_unc13a",
                      color = 'rs12608932',
                      add = "reg.line", size = 3
                      ) +
    ylab("UNC13A CE PSI ") +
    xlab("STMN2 Cryptic PSI ") +
  stat_cor(aes( x = stmn_2_cryptic_psi_leaf,
                      y = unc13a_cryptic_leaf_psi,
                      color = rs12608932),
           method = 'spearman',
           cor.coef.name = 'rho',
           show.legend = FALSE,
           size = 14) +
    scale_color_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  theme(legend.title = element_blank()) +
  theme(text = element_text(size = 24),legend.text = element_text(size = 32)) +
      ylab(expression(paste("Lo", g[10], "UNC13A CE PSI"))) +
      xlab(expression(paste("Lo", g[10], "STMN2 CE PSI"))) +
   ggtitle("intronic SNP (rs12608932) genotype")

```{r}
ggpubr::ggarrange(ce_snp,in_snp)
```

>>>>

## Systematic differences in  (read length) between cases and controls

```{r sequences and case/controls}
# library size 
#llumina HiSeq 2500 (125 bp paired end) or an Illumina NovaSeq (100 bp paired end). 
case_control_sequencing <- clean_data_table %>%
  filter(tissue_clean %in% c("Frontal_Cortex", 
                             "Lumbar_Spinal_Cord", 
                             "Cervical_Spinal_Cord", 
                             "Motor_Cortex", 
                             "Temporal_Cortex",
                             "Cerebellum")) %>% 
  filter(sequencing_platform != "")

quick_chiq = function(tbl){

    if(length(unique(tbl$sequencing_platform)) < 2){
      return(NA)
    }
    comparison_table = table(disease = tbl$disease_group2, 
                             sequencing_platform = tbl$sequencing_platform)
    print(comparison_table)

    p_value = chisq.test(comparison_table) %>%  broom::tidy() %>% pull(p.value)
    browser()
    print(p_value)

    return(p_value)
}

case_control_sequencing %>% 
  group_by(tissue_clean) %>% 
  nest()  %>% 
  mutate(chiq_pvalue = map_dbl(data, quick_chiq))

unc13a_data_fisher$data = NULL

unc13a_sequencing_platform_pct %>%
  ggplot(aes(x = plot_name, y = detection )) + 
  geom_col(fill = "firebrick") +
  labs(title = "UNC13A CE detection and sequencing platform", 
       y = "UNC13A CE detected",x = element_blank(), subtitle = "Fisher exact test") + 
  facet_wrap(~disease_group2 + tissue_clean,scales = 'free_x') +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  geom_text(aes(x = 1.5, y = 1.05, label = paste0("p = ", signif(fisher_pvalue,digits = 2) ) )) +
  theme(legend.text = element_text(size = 15)) +
  ggpubr::theme_pubr()
 # scale_y_continuous(expand = c(0,0) ) 
```

## Effect of sequencing machine (read length) on CE discovery

@@

    if(length(unique(tbl$sequencing_platform)) < 2){
      return(NA)
    }
    comparison_table = table(unc13a = tbl$unc13a_detected, 
                             sequencing_platform = tbl$sequencing_platform)
    p_value = fisher.test(comparison_table)$p.value

    return(p_value)
}

unc13a_data_fisher = unc13a_sequencing_platform %>% 
  filter(tissue_clean != "Thoracic_Spinal_Cord") %>% 
  group_by(disease_group2,tissue_clean) %>% 
  nest() %>% 
  mutate(fisher_pvalue = map_dbl(data, quick_fisher))

unc13a_data_fisher$data = NULL

@@

unc13a_sequencing_platform_pct %>%
  ggplot(aes(x = plot_name, y = detection )) + 
  geom_col(fill = "firebrick") +
  labs(title = "UNC13A CE detection and sequencing platform", 
       y = "UNC13A CE detected",x = element_blank(), subtitle = "Fisher exact test") + 
  facet_wrap(~disease_group2 + tissue_clean,scales = 'free_x') +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  geom_text(aes(x = 1.5, y = 1.05, label = paste0("p = ", signif(fisher_pvalue,digits = 2) ) )) +
  theme(legend.text = element_text(size = 15)) +
  ggpubr::theme_pubr()
 # scale_y_continuous(expand = c(0,0) ) 
```
## Effect of library size on CE discovery

```{r unc detection by library size  }
# library size 
force_colors = c("#F8766D", "#A3A500", "#00BF7D", "#00B0F6", "#E76BF3")
names(force_colors) = c("Control","ALS \n non-TDP","ALS-TDP","FTLD \n non-TDP","FTLD-TDP")

plot_list = list()

lib_comps = c("Cervical_Spinal_Cord", "Frontal_Cortex", 
              "Lumbar_Spinal_Cord", "Temporal_Cortex",
              "Motor_Cortex", "Cerebellum")

plot_list = list()
for(t in 1:length(lib_comps)){
  plt = clean_data_table %>%
     filter(tissue_clean == lib_comps[t]) %>% 
    mutate(inclusion_reads = UNC13A_3prime_leaf + UNC13A_5prime_1_leaf) %>% 
    mutate(unc13a_detected = ifelse(inclusion_reads > 0, yes = "+", no = "-")) %>% 
    mutate(disease_group2 = fct_relevel(disease_group2, "Control")) %>% 
    ggplot(aes(x = disease_group2,y = log10(library_size),fill = disease_group2)) + 
    geom_boxplot(colour = "black", outlier.colour = NA) +
    geom_point(pch = 21, size = 2, alpha = 0.9, position = position_jitter(width = 0.2, height = 0) ) + 
    facet_wrap(~ tissue_clean,scales = 'free_x') + 
    # ggpubr::stat_compare_means(label = "p.format", label.x.npc = "center", method = "wilcox" ) +
    ggpubr::stat_compare_means(label = "p.signif",
                               label.x.npc = "center",
                               method = "wilcox",
                               comparisons = list(
                                                  c("Control","ALS-TDP"),
                                                  c("ALS \n non-TDP","ALS-TDP"))) +
      ggpubr::stat_compare_means(label = "p.signif", 
                               label.x.npc = "center", 
                               method = "wilcox",
                               comparisons = list(
                                                  c("Control","FTLD-TDP"),
                                                  c("FTLD-TDP","FTLD \n non-TDP"))) + 
    labs(y = "log10 library size", fill= "UNC13A CE detected", x = element_blank()) +
    theme(axis.text.x = element_text(size = 15)) + 
    ggpubr::theme_pubr() + 
    scale_fill_manual(values = force_colors) +
            theme(axis.ticks.x = element_blank(),
              axis.text.x = element_blank(),
              legend.position = "none")

  plot_list[[t]] <- plt
}

cowplot::plot_grid(plotlist = plot_list)
```

```{r rin discovery}
force_colors = c("#F8766D", "#A3A500", "#00BF7D", "#00B0F6", "#E76BF3")
names(force_colors) = c("Control","ALS \n non-TDP","ALS-TDP","FTLD \n non-TDP","FTLD-TDP")

plot_list = list()

lib_comps = c("Cervical_Spinal_Cord", "Frontal_Cortex", 
              "Lumbar_Spinal_Cord", "Temporal_Cortex",
              "Motor_Cortex", "Cerebellum")

plot_list = list()
for(t in 1:length(lib_comps)){
    if(grepl("Cord",lib_comps[t]) | lib_comps[t] == "Motor_Cortex"){
        groups = c("Control","ALS-TDP","ALS \n non-TDP")
    }else if(lib_comps[t] %in% c("Frontal_Cortex","Temporal_Cortex")){
        groups = c("Control","FTLD-TDP","FTLD \n non-TDP")
    }else{
        groups = c("ALS-TDP", "Control", "ALS \n non-TDP", "FTLD-TDP", "FTLD \n non-TDP")
    }

    plt = clean_data_table %>%
        filter(tissue_clean == lib_comps[t]) %>% 
        mutate(disease_group2 = fct_relevel(disease_group2, "Control")) %>% 
        filter(disease_group2 %in% groups) %>%

        ggplot(aes(x = disease_group2,y = rin,fill =disease_group2 )) + 
        geom_boxplot(colour = "black", outlier.colour = NA) +
        geom_point(pch = 21, size = 2, alpha = 0.9, position = position_jitter(width = 0.2, height = 0) ) + 
        facet_wrap(~ tissue_clean,scales = 'free_x') + 
        # ggpubr::stat_compare_means(label = "p.format", label.x.npc = "center", method = "wilcox" ) +
        ggpubr::stat_compare_means(label = "p.signif",
                                   label.x.npc = "center",
                                   method = "wilcox",
                                   comparisons = list(
                                       c("Control","ALS-TDP"),
                                       c("ALS \n non-TDP","ALS-TDP"))) +
        ggpubr::stat_compare_means(label = "p.signif", 
                                   label.x.npc = "center", 
                                   method = "wilcox",
                                   comparisons = list(
                                       c("Control","FTLD-TDP"),
                                       c("FTLD-TDP","FTLD \n non-TDP"))) + 
        labs(y = "RIN", x = element_blank()) +
        theme(axis.text.x = element_text(size = 15)) + 
        ggpubr::theme_pubr() + 
        theme(axis.ticks.x = element_blank(),
              axis.text.x = element_blank(),
              legend.position = "none")

    plot_list[[t]] <- plt
}

cowplot::plot_grid(plotlist = plot_list,ncol = 2)    
```

```{r unc13a ce and UNC13B_TPM}
## effect of RIN?
clean_data_table %>%
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP", "ALS-TDP")) %>%
  add_count(tissue_clean,disease_group2) %>% 
  mutate(plot_name = glue::glue("{disease_group2} \n ({n})")) %>% 
  mutate(inclusion_reads = UNC13A_3prime_leaf + UNC13A_5prime_1_leaf) %>% 
  mutate(unc13a_detected = ifelse(inclusion_reads > 0, yes = "+", no = "-") ) %>% 
  ggplot(aes(x = plot_name, fill = unc13a_detected,y = UNC13B_TPM )) + 
  geom_point(size = 2,show.legend = F,pch = 21, position = position_jitterdodge(dodge.width=1,jitter.width = 0.3))+
  geom_boxplot(outlier.colour = NA) +
  labs(title = "UNC13A CE detection and UNC13B TPM",subtitle = "Wilcox test") + 
  facet_wrap(~ tissue_clean,scales = 'free') + 
  ggpubr::stat_compare_means(label = "p.signif") +
  labs(y = "UNC13B TPM", x = "UNC13A CE detection") +
  theme(axis.text.x = element_text(size = 15)) +
  ggpubr::theme_pubr() +
  ggpubr::stat_compare_means(label = "p.format", label.x.npc = "center",label.y.npc = 0.9)
```

## Celltype composition between cases and controls

```{r}
force_colors = c("#F8766D", "#A3A500", "#00BF7D", "#00B0F6", "#E76BF3")
names(force_colors) = c("Control","ALS \n non-TDP","ALS-TDP","FTLD \n non-TDP","FTLD-TDP")

plot_list = list()

lib_comps = c("Cervical_Spinal_Cord", "Frontal_Cortex", 
              "Lumbar_Spinal_Cord", "Temporal_Cortex",
              "Motor_Cortex", "Cerebellum")

for(t in 1:length(lib_comps)){

    if(grepl("Cord",lib_comps[t]) | lib_comps[t] == "Motor_Cortex"){
        groups = c("Control","ALS-TDP","ALS \n non-TDP")
    }else if(lib_comps[t] %in% c("Frontal_Cortex","Temporal_Cortex")){
        groups = c("Control","FTLD-TDP","FTLD \n non-TDP")
    }else{
        groups = c("ALS-TDP", "Control", "ALS \n non-TDP", "FTLD-TDP", "FTLD \n non-TDP")
    }

    plt = cell_types %>% 
        left_join(clean_data_table[,.(sample,
                                      UNC13A_3prime_leaf,
                                      UNC13A_5prime_1_leaf,
                                      disease_group2,
                                      disease_tissue)], by = 'sample') %>%
        filter(!is.na(disease_group2)) %>% 
        unique() %>% 
        filter(tissue_clean == lib_comps[t]) %>% 
        filter(disease_group2 %in% groups) %>% 
        mutate(disease_group2 = fct_relevel(disease_group2, "Control")) %>% 
        ggplot(aes(x = disease_group2,y = deconv,fill =disease_group2 )) + 
        geom_boxplot(colour = "black", outlier.colour = NA) +
        facet_wrap(~cell,scales = 'free_x',nrow = 1) +
        ggpubr::stat_compare_means(label = "p.signif", 
                                   label.x.npc = "center", 
                                   method = "wilcox",
                                   comparisons = list(
                                       c("Control","FTLD-TDP"),
                                       c("FTLD-TDP","FTLD \n non-TDP"))) +
        ggpubr::stat_compare_means(label = "p.signif",
                                   label.x.npc = "center",
                                   method = "wilcox",
                                   comparisons = list(
                                       c("Control","ALS-TDP"),
                                       c("ALS \n non-TDP","ALS-TDP"))) +
        ggtitle(lib_comps[t]) + 
        labs(fill = element_blank(),x = element_blank()) + 
        geom_point(pch = 21, size = 2, alpha = 0.9, position = position_jitter(width = 0.2, height = 0) ) + 
        ggpubr::theme_pubr() +
        theme(axis.ticks.x = element_blank(),
              axis.text.x = element_blank(),
              legend.position = "none") + 
        scale_fill_manual(values = force_colors)
plot_list[[t]] <- plt

cowplot::plot_grid(plotlist = plot_list,ncol = 2)

@@

@@

```{r onlyshort}
only_short_plotter = boxplot_table %>%
    filter(tissue_clean %in%
               c("Frontal Cortex",
                 "Lumbar Spinal Cord",
                 "Cervical Spinal Cord",
                 "Motor Cortex",
                 "Temporal Cortex",
                 "Cerebellum") )%>%
    group_by(disease_group2,tissue_clean) %>%
    mutate(n_sample = n_distinct(sample)) %>%
    ungroup() %>%
    mutate(disease_group2 = gsub("Control", " Control",disease_group2)) %>%
    mutate(detection_name = glue::glue("{disease_group2} \n ( {n_sample} )"))  %>%
    mutate(tissue_clean = fct_relevel(tissue_clean, "Cervical Spinal Cord",
                                      "Frontal Cortex",
                                      "Lumbar Spinal Cord",
                                      "Temporal Cortex",
                                      "Motor Cortex"))

comps = only_short_plotter %>% pull(detection_name) %>%
  unique() %>%
  combn(.,2,simplify = F)

only_short_plotter %>% 
    ggplot(aes(x = detection_name,
               y = inclusion_reads * 10^6,
               fill ="red")) +
    geom_boxplot(show.legend = F,position = position_dodge(preserve = "single",width = 1),outlier.colour = NA) +
    geom_point(size = 2,show.legend = F,pch = 21, position = position_jitterdodge(dodge.width=1,jitter.width = 0.3))+
    ggplot2::facet_wrap(vars(tissue_clean),scales = "free_x",nrow = 3) +
    ylab("UNC13A cryptic \n reads per million") +
    theme(text = element_text(size = 12)) +
    xlab("") +
    scale_fill_manual(values = colorblind_pal()(4)[2:4]) +
    theme_bw() +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    theme(text = element_text(size = 18))  +
    theme(legend.position = "bottom")
```

@@

## Correlation UNC13A PSI and STMN2 PSI with genotype effect - concordants samples

@@

clean_data_table %>%
  filter(!(rs12973192 == "C/G" & rs12608932 == "C/C")) %>%
  mutate(snp_status = case_when(rs12973192 == "C/C" ~ "healthy/healthy",
                                rs12973192 == "C/G" ~ "healthy/risk",
                                rs12973192 == "G/G" ~ "risk/risk")) %>% 
  filter(disease_tissue == T) %>%
  filter(junction_reads_stmn2 >= 30) %>%
  filter(junction_reads_unc13a >= 30) %>%
  filter(grepl("Cortex",tissue_clean)) %>%
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>%
    mutate(rs12973192 = fct_relevel(rs12973192,
                              "C/C", "C/G", "G/G")) %>%
  filter(!grepl("Cord",tissue_clean)) %>%
  mutate(log10_stmn2 = log10(stmn_2_cryptic_psi_leaf)) %>%
    mutate(log10_unc13a = log10(unc13a_cryptic_leaf_psi)) %>%
    ggpubr::ggscatter(.,
                      x = "log10_stmn2",
                      y = "log10_unc13a",
                      fill = 'snp_status',
                      color = 'black', 
                      size = 3,shape = 21,
                      ) +
    ylab("UNC13A CE PSI ") +
    xlab("STMN2 Cryptic PSI ") +
  geom_smooth(method = 'lm',aes(color = snp_status),se = F) + 
  stat_cor(aes( x = stmn_2_cryptic_psi_leaf,
                      y = unc13a_cryptic_leaf_psi,
                      color = snp_status),
           method = 'spearman',
           cor.coef.name = 'rho',
           show.legend = FALSE,
           size = 14) +
    scale_color_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
      scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +

  theme(legend.title = element_blank()) +
  theme(text = element_text(size = 24),legend.text = element_text(size = 32)) +
    ylab(expression(paste("Lo", g[10], "UNC13A CE PSI"))) +
      xlab(expression(paste("Lo", g[10], "STMN2 CE PSI")))

@@
